---
title: "Paper - SQL"
format: html
editor: visual
---

## Running Code

```{r}
setwd("C:/Users/lihin/OneDrive/מסמכים/MA/קורסים/מיומנות")

 con_chocolate <- DBI::dbConnect(drv = RSQLite::SQLite(),
 dbname = "chocolate.sqlite")
```

**Q1**: What the boss wanted was a table with two columns: names of sale representatives and the total amount of candy bars they sold. Specifically, he wanted this for 2022 and for sale representatives who joined the company in 2010.

```{sql, connection = con_chocolate, output.var = "Q1_output"}

SELECT salesreps.Name, SUM(orders.amount) AS total_candy_bars_sold
 FROM salesreps INNER JOIN orders USING (srid)
 WHERE
 orders.sale_date BETWEEN '2022-01-01' AND '2022-12-31'
 AND salesreps.year_joined = 2010
 GROUP BY salesreps.Name;
```

The answer is a table containing three sale representatives, and their the total candy bars the sold.

```{r}
print(Q1_output)
```

**Q2**: A frequency table.

The inner brackets check how many orders each customer has made. The outer brackets check the frequency of the different order quantities, and store this as N. The result is a table containing the numbers of orders that have been made and their frequency.

```{sql, connection = con_chocolate, output.var = "Q2_output"}

SELECT total_number_of_order, COUNT(total_number_of_order) AS N
FROM (
SELECT COUNT(orders.cid) AS total_number_of_order
FROM orders
GROUP BY cid)  
GROUP BY total_number_of_order
```

```{r}
print(Q2_output)
```

**Q3**: The best-selling candy bar in the first quarter is "Coconut Carve". Also, the sales representative who sold this bar the most in the second quarter is Christopher Hess.

```{sql, connection = con_chocolate, output.var = "Q3_output"}

WITH sales_summary AS (
SELECT SUM(orders.amount) AS total_sales, orders.pid AS candy, products.candy_names AS names 
FROM orders
INNER JOIN products 
ON orders.pid = products.pid
WHERE orders.sale_date BETWEEN '2022-01-01' AND '2022-03-31'
GROUP BY orders.pid
), 
best_candy AS(
SELECT candy, names
FROM sales_summary
WHERE total_sales = (
    SELECT MAX(total_sales)
    FROM sales_summary)
),
best_sales_rep AS(
select salesreps.Name, orders.srid, sum(orders.amount) AS total
FROM orders
INNER JOIN salesreps 
ON orders.srid = salesreps.srid
WHERE orders.pid = (SELECT candy FROM best_candy)
AND orders.sale_date BETWEEN '2022-04-01' AND '2022-06-31'
GROUP BY orders.srid
ORDER BY total DESC
LIMIT 1
)

SELECT 
    (SELECT names FROM best_candy) AS best_candy,
    (SELECT Name FROM best_sales_rep) AS best_sales_rep

```
